\section{Part 3: The Spider's Web}
At this point, the players are following up on leads they have learned from in Phandalin. The players should have the following quests available to them:

\begin{description}
	\item[Agatha's Lair] Sister Garaele wants the players to seek out the banshee Agatha north of the ruins of Conyberry and ask about Bowgentle's spell book.
	\item[Old Owl Well] Daran Edermath wants someone to investigate what is happening near the ruins of Old Owl Well.
	\item[Thundertree] Qelline Alderleaf suggested the players consult Reidoth the druid at the ruins of Thundertree to ask about the location of Cragmaw Castle or the Wave Echo cave.
	\item[Wyvern Tor] Harbin Wester wants players to chase away the orc encampment near Wyvern Tor.
	\item[Gundren Rockseeker] Sildar Hallwinter wants to continue the search for Gundren, Cragmaw Castle, and find the map of the Wave Echo cave.
\end{description}

\subsection{\underline{The Tribor Trail and Other Wilderness Encounters}}
While traveling to various locations, encounters may happen. Players travel 24 miles per day. Roll a d20 once per day and once per night to determine if an encounter happens (17-20). Upon an encounter, roll a d12 to determine which of these encounters happen:

\begin{description}
	\item[day: 1-2 / night: 1-3] Stirges (1d8 + 2)
	\item[day: - / night: 4] Ghouls (1d4 + 1)
	\item[day: 3-4 / night: -] Ogre (1)
	\item[day: 5-6 / night: 5] Goblins (1d6 + 3)
	\item[day: 7-8 / night: 6] Hobgoblins (1d4 + 2)
	\item[day: 9-10 / night: 7-8] Orcs (1d4 + 2)
	\item[day: 11 / night: 9-10] Wolves (1d4 + 2)
	\item[day: 12 / night: 11-12] Owlbear (1)
	
\end{description} 

