\section{Part 2: Phandalin}
Players arrive in the town of Phandalin which is being threatened by a gang called the Redbrands, headed by a mysterious figure called Glasstaff. Phandalin is where the players will gather information about the story and possibly get some side-quests.

\subsection{\underline{The Town of Phandalin}}

\subsubsection*{\underline{Stonehill Inn}}
The Stonehill inn is the local inn for the town of Phandalin. It has six rooms available (Sildar takes one). The proprietor is Toblen Stonehill and is a good source of information about Phandalin, the Redbrands. The people in the inn have some interesting gossip and information to share:

\begin{description}	
	\item[Narth, old farmer] Sister Garaele has left town recently and came back wounded and exhausted.
	\item[Freda, a weaver] The Redbrands harass almost every business in town except for the miner's exchange, they seem to be scared of Halia.
	\item[Elsa, gossipy barmaid] Daran Edermath at the orchard, is a former adventurer.
	\item[Lanar, a miner] Orcs have been seen on the east end of the Triboar trail. Harbin Wester is looking for people to drive them away.
	\item[Trilena, innkeeper's wife] Thel Dendrar, local woodcarver, was murdered by the Redbrands because he stood up to them when they harassed his wife. His wife, daughter, and son have gone missing.
	\item[Pip, innkeeper's son] Qelline's son is friends with Pip. He told Pip about a secret Redbrand tunnel in the woods.
\end{description}

\subsubsection*{\underline{Barthen's Provisions}}
Barthen's, run by Elmar Barthen, is the biggest trading post in Phandalin. It sells most common items, anything that is less than 25gp.

Elmar is sad to hear the news about Gundren, and is familiar with his work. He is annoyed with the Redbrands and tells the player they like to hang out at the Sleeping Giant.

\emph{\underline{Reward}: Elmar gives every player 10gp upon delivering the supplies.}

\subsubsection*{\underline{Edermath Orchard}}
Daran Edermath is concerned with the Redbrands and their leader Glasstaff, and knows they hang out by the Sleeping Giant and have a safe house under Tresendar Manor.

\emph{\underline{Quest: Old Owl Trouble}. Prospectors at the ruins of Old Owl Well have been chased from the area by undead and strange magical phenomenon. }


\subsubsection*{\underline{Lionshield Coster}}
The Lionshield Coster is owned by the Lionshield merchant company. The ship and sell finished goods and this is the place to get weapons and armor. 

\emph{\underline{Reward}: If the stolen goods found in Cragmaw hideout are returned here, Linene gives the players a 50gp reward, and promises to help them in anyway she can.}

\subsubsection*{\underline{Miner's Exchange}}
This is where miners come to trade their valuables. The guildmaster is a human woman named Halia Thornton, who desires to run the town and the Redbrands (a DC 15 insight check reveals her true motives). 

\emph{\underline{Quest: Halia's Job Offer}. Halia promises 100gp for the players to eliminate Glasstaff and returns with evidence. }

\subsubsection*{\underline{Alderleaf Farm}}
The players meet Qelline Alderleaf. She can provide a lot of information about the town and the Redbrands. She is willing to let the players stay in her hayloft if they prefer not to stay at the inn. Her son, Carp saw a tunnel which he believes leads to the secret hideout of the Redbrands, underneath Tresendar Manor.

\emph{\underline{Quest: Reidoth the Druid}. Reidoth, a druid studying the ruins of Thundertree, has the information about Cragmaw Castle and possibly the Wave Echo cave the players are looking for. }

\subsubsection*{\underline{Shrine of Luck}}
Phandalin's only temple is a little shrine to the goddess of luck and good fortune, Tymora, under the care of Sister Garaele. Garaele wants to see the Redbrands leave town, she's a member of the Harpers, a scattered network of adventurers that fight for justice.

\emph{\underline{Quest: The Banshee's Bargain}. Bring the banshee Agatha a suitable gift and ask her for information about the location of a spellbook belonging to a legendary mage named Bowgentle. The reward for the player's effort is three potions of healing. }


\subsubsection*{\underline{Townmaster's Hall}}
Harbin Wester was elected as Phandalin's only form of government. The hall has a small jail used to jail Redbrands and Glasstaff, if captured.

\emph{\underline{Quest: Orc Trouble}. Harbin wants people to clear a band of orcs near Wyvern Tor. The reward is 100gp.}

\emph{\underline{Quest: Finding Cragmaw Castle}. Sildar offers 500gp for the players to find the location of Cragmaw Castle and drive off the chieftain. }

\emph{\underline{Quest: Finding Iarno}. Iarno Albrek disappeared recently while exploring the area around Tresendar Manor. Sildar wants him found, dead or alive.  }

\subsection{\underline{Redbrand Ruffians Hideout}}

\subsubsection*{\underline{Sleeping Giant Tap House}}
The Sleeping Giant is where the players first encounter and fight some Redbrand ruffians. \textbf{Four ruffians} taunt and attack the players.

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
		\begin{description}
			\item[Redbrand Ruffian]
			AC: 14, HP: 16, Speed: 30ft.
			\\ STR[11](+0) 
			\\ DEX[14](+2)
			\\ CON[12](+1)
			\\ INT[9](-1)
			\\ WIS[9](-1)
			\\ CHA[11](+0) 
			\\ Intimidation +2, Passive Perception: 9, 100xp
			\\ \textbf{Multiattack}: The ruffian makes two melee attacks.
			\\ \textbf{Shortsword}: +4 to hit, 1d6+2 piercing
		\end{description}
\end{minipage}}
\break

\subsubsection*{\underline{Tresendar Manor}}
Tresendar Manor is an ancient, abandoned, ruined, large home owned by the Tresendar family, which the Redbrands have converted the cellar into their hideout. Stairs from what once was the kitchen leads down to the cellar \emph{area 1}.

Secret doors require a DC 15 perception check to discover, or a DC 10 if the players are actively looking at the walls.

\subsubsection*{\underline{1. Cellar}}
Nothing in this room gives away the presence of the Redbrands. The barrels contain salted pork, beef, flour, sugar, apples, and ale. Heavy investigation of this area will alert the ruffians in \emph{area 2}.

\emph{\underline{Treasure}: The 10 ft. deep cistern contains a waterproof satchel hanging from a rope which contains \textbf{a potion of healing (heals 2d4+2 hit points)} and \textbf{a potion of invisibility (1hour, 50gp)}}.

\subsubsection*{\underline{2. Barracks}}
\textbf{Three ruffians} are resting in this room. If the players make too much noise in \emph{area 1}, the ruffians will be ready to surprise the players.

\emph{\underline{Treasure}: 27 gp, 28 sp, two garnets worth 10 gp each. Three scarlet cloak hang from the bunks.}

\subsubsection*{\underline{3. Trapped Hall}}
There is a trap in the middle of the hall. A DC 15 perception or investigation check is required to spot the trap. Maneuvering around the trap once discovered requires a DC 10 acrobatics check. Triggering or failing the acrobatics check requires a DC 15 dexterity saving throw to catch the edge. Failing the saving throw, player falls 20 feet into the pit and takes 2d6 bludgeoning damage.

\emph{\underline{Reward}: 100 XP for surviving the trap.}

\subsubsection*{\underline{4. Tresendar Crypts}}
\textbf{Three skeletons} are guarding the door that leads to \emph{area 5}. They attack the players unless they are wearing the scarlet cloaks or speak the secret password "Illefarn".

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
		\begin{description}
			\item[Skeleton]
			AC: 13, HP: 13, Speed: 30ft.
			\\ STR[10](+0) 
			\\ DEX[14](+2)
			\\ CON[15](+2)
			\\ INT[6](-2)
			\\ WIS[8](-1)
			\\ CHA[5](-3) 
			\\ Vulnerability: bludgeoning
			\\ Immunity: poison
			\\ Darkvision 60 ft., Passive Perception: 9, 50xp
			\\ \textbf{Shortsword}: +4 to hit, 1d6+2 piercing
			\\ \textbf{Shortbow}: +4 to hit, 1d6+2 piercing
		\end{description}
\end{minipage}}
\break

\emph{\underline{Treasure}: Amid the bones in each sarcophagus is a platinum signet ring (50 gp).}

\subsubsection*{\underline{5. Slave Pens}}
\textbf{Two ruffians} are waiting and trying to surprise the players that come in. Three human commoners are being held prisoner (Mirna Dendrar and her two teenage children). Cell doors can be opened with a DC 10 sleight of hand lock pick, or forced open with a DC 22 strength check.

\emph{\underline{Quest: Mirna's Heirloom}. Mirna has no reward for the players but possibly has a valuable heirloom in southeast Thundertree, in an abandoned alchemy shop that was overrun with undead. }

\emph{\underline{Reward}: 100 XP if the Dendrars make it back to town alive.}

\subsubsection*{\underline{6. Armory}}
Armory stockpile of weapons for the Redbrands. A rack in the room holds twelve spears, six shortswords, four longswords, six light crossbows, eight quivers (20 bolts).

\subsubsection*{\underline{7. Storeroom and Work Area}}
This is where the Redbrands keep their stolen goods. There's nothing much of value other then a stack of thirty beaver pelts worth 2 gp each.

\subsubsection*{\underline{8. Crevasse}}
A \textbf{nothic}, lured by the magical effect emanating from the crevass, lurks nears the west ends of the two bridges. He hides behind the large columns and uses \emph{Weird Insight} to discern players secrets. He would rather not fight and negotiate with the player, through telepathy, asking for food.

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
		\begin{description}
			\item[Nothic]
			AC: 15, HP: 45, Speed: 30ft.
			\\ STR[14](+2) 
			\\ DEX[16](+3)
			\\ CON[16](+3)
			\\ INT[13](+1)
			\\ WIS[10](+0)
			\\ CHA[8](-1)
			\\ Arcana +3, Insight +4, Perception +2, Stealth +5
			\\ Truesight 120 ft., Passive Perception: 12, 450xp
			\\ \textbf{Multiattack}: Makes two attacks with its claws
			\\ \textbf{Claws}: +4 to hit, 1d6+3 slashing
			\\ \textbf{Rotting Gaze} 30 ft., DC 12 constitution saving throw, 3d6 necrotic
			\\ \textbf{Weird Insight} Target must contest deception check with nothic's insight check. If nothic wins, it learns one fact about the target.
			\\ \textbf{Keen Sight} Has advantage on perception checks 
		\end{description}
\end{minipage}}
\break

The southern bridge is ridged to collapse when stepped on (DC 15 investigation check reveals this). Falling into the crevasse deals 2d6 bludgeoning damage. In the crevasse is the body of Thel Dendrar (Mirna's husband), and a wooden chest. 

\emph{\underline{Reward}: 450 XP for defeating or negotiating with the nothic.}

\emph{\underline{Treasure}: Wooden chest contains: 160 sp, 120 gp, five malachite gems (15 gp each), two \textbf{potions of healing}, a \textbf{scroll of augury}, and a \textbf{+1 longsword}.}

\subsubsection*{\underline{9. Guard Barracks}}
The room has \textbf{Three bugbears} (leader is named Mosk) working for the Black Spider, sent to keep an eye on the Redbrands. They are harassing a \textbf{goblin} named Droop, he falls unconscious at the sight of the players, and if revived, he hides and avoids the fight.

\emph{\underline{Treasure}: 33 sp, and Mosk's eye patch is made of semiprecious stones worth 50 gp.}

\subsubsection*{\underline{10. Common Room}}
\textbf{Four Redbrand Ruffians} are distracted, drinking and playing knucklebones, so the players can surprised them.

\emph{\underline{Treasure}: 75cp, 55 sp, 22 ep, 15 gp, gold earring set with a ruby (30 gp).}

\subsubsection*{\underline{11. Wizard's Workshop}}
A rat (AC 10, 1 hit point) which is Iarno's familiar, runs to \emph{area 12} to warn him when the players enter. The room has a bunch of alchemy tools and apparatus (not worth much). Some books and scrolls detailing alchemical processes to make potions of invisibility. Also another book written in dwarvish describes the lost mine of Phandelver, and Phandelver's Pact.

\subsubsection*{\underline{12. Glasstaff's Quarters}}
If the players surprise Glasstaff (Iarno), either by killing the rat before it warns him, or through the secret entrance to his quarters, they can fight him.

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
		\begin{description}
			\item[Evil Mage]
			AC: 12, HP: 22, Speed: 30ft.
			\\ STR[9](-1) 
			\\ DEX[14](+2)
			\\ CON[11](+0)
			\\ INT[17](+3)
			\\ WIS[12](+1)
			\\ CHA[11](+0)
			\\ Saving throws Int +5, Wis +3
			\\ Skills Arcana +5, History +5
			\\ Passive Perception: 11, 200xp
			\\ \textbf{Spellcasting}: 4th level, DC 13 Int save, +5 to hit with attacks
			\\ \textbf{Cantrips}: light, mage hand, shocking grasp
			\\ \textbf{1st Level}: charm person, magic missile
			\\ \textbf{2nd Level}: hold person, misty step
			\\ \textbf{Quarterstaff}: +1 to hit, 1d8-1 bludgeoning 
		\end{description}
\end{minipage}}
\break

Iarno has a \textbf{staff of defense} (+1 AC, 10 charges, cast \emph{mage armor} for 1 charge or \emph{shield} for 2 charges). If Iarno is:

\begin{description}
	\item[Surprised] The players can fight him. If he is reduced to 8 or fewer hit points, he surrenders, valuing his life over anything.
	\item[Not surprised, warned] Iarno grabs his staff and notes, and escapes through the secret door, to \emph{area 7, 8, and 1}. If the nothic is still alive, he instructs it to stop the players. In \emph{area 1}, he grabs the hidden satchel in the cistern if it's still there.
\end{description}

The black spider letter was left on the desk (read from the book). Sildar Hallwinter arranges for Iarno to be incarcerated in the Phandalin townmaster's hall.

\emph{\underline{Treasure}: 180 sp, 130 gp, silk pouch containing five carnelians (10 gp), two peridots (15 gp), one pearl (100 gp), a \textbf{scroll of charm}, a \textbf{scroll of fireball}, and Iarno's \textbf{staff of defense}}

\subsection{\underline{NPCs}}
\begin{description}
	\item[Carp Alderleaf] Ten year old halfling, son of Qelline, wants to become an adventurer, knows the location of the Redbrand hideout.
	\item[Daran Edermath] Fit, silver-haired half-elf, fighter, lives in a cottage by the apple orchard.
	\item[Elmar Barthen] Lean balding, 50 year old human owner of Barthen's Provisions.
	\item[Halia Thornton] Human female guildmaster of the Miner's guild, has ambitions to become leader of Phandalin and the Redbrands.
	\item[Harbin Wester] Fat, pompous human banker and townmaster of Phandalin, who is afraid of the Redbrands.
	\item[Iarno Albrek (Glasstaff)] Short, dark bearded human male wizard, fellow member and traitor to the Lord's Alliance and secret leader of the Redbrands.
	\item[Linene Graywind] Runs the Lionshield Coster, rewards players for returning the stolen goods from the Cragmaw Hideout.
	\item[Mirna Dendrar] Human female being held in the Redbrand hideout. Her husband was murdered after defying them. 
	\item[Sildar Hallwinter] Older human fighter hired by Gundren to escort him in his travels.
	\item[Toblen Stonehill] Friendly young human male Proprietor of the Stonehill Inn. Came to Phandalin to prospect but decided to run the inn instead. He is upset about the Redbrands, and that Harbin Wester hasn't done anything about them.
	\item[Qelline Alderleaf] Forty-five year old halfling, wise and hospitable female, owner and farmer of Alderleaf farm. She knows everything about the town.
\end{description}