	\section{Part 1: Goblin Arrows}

While on the road to Phandalin, on the Triboar trail, the players get ambushed by Cragmaw tribe \textbf{goblins}, whom have captured Gundren and Sildar and brought back to their hideout. The players deal with the ambush and follow the trail to the Cragmaw hideout. Once rescued, Sildar informs them of the background and that Gundren and the map were taken to Cragmaw Castle.



\subsection*{\underline{Goblin Ambush}}
On the Triboar trail, \textbf{four goblins} hide and attempt to ambush (roll for stealth) the players. Two of the goblins rush for melee attacks, the other two use their shortbows. The last surviving goblin attempts to flee and joins the other goblins at the Cragmaw hideout (\emph{area 2}).

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
\begin{description}
	\item[Goblins] 
	AC: 15, HP: 7, Speed: 30ft.
	\\ STR[8](-1) 
	\\ DEX[14](+2)
	\\ CON[10](+0)
	\\ INT[10](+0)
	\\ WIS[8](-1)
	\\ CHA[8](-1) 
	\\ Stealth +6, Passive Perception: 9, 50xp
	\\ \textbf{Scimitar}: +4 to hit, 1d6+2 slashing
	\\ \textbf{Shortbow}: +4 to hit, 1d6+2 piercing
\end{description}
\end{minipage}}
\break

\subsection*{\underline{Cragmaw Hideout}}
\subsubsection*{\underline{1. Cave Mouth}}
Goblins are suppose to keep watch, but are distracted in \emph{area 2}.

\emph{\underline{Reward}: 75xp for finding the Cragmaw Hideout.}

\subsubsection*{\underline{2. Goblin Blind}}
\textbf{Two goblins} (with a possible third) are guarding the entrance to the cave. Surviving goblin will attempt to run into the cave and release the wolves from \emph{area 3}.

\subsubsection*{\underline{3. Kennel}}
\textbf{Three wolves} are chained up in this area, and will attempt a DC 15 (10 on failure) strength check every round to attempt to break free from the chains.

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
\begin{description}
	\item[Wolves]
	AC: 13, HP: 11, Speed: 40ft.
	\\ STR[12](+1) 
	\\ DEX[15](+2)
	\\ CON[12](+1)
	\\ INT[3](-4)
	\\ WIS[12](+1)
	\\ CHA[6](-2) 
	\\ Perception +3, Stealth +4, Passive Perception: 13, 50xp
	\\ \textbf{Keen Hearing and Smell}: advantage on perception checks.
	\\ \textbf{Pack Tactics}: advantage on attack when another wolf is around.
	\\ \textbf{Bite}: +4 to hit, 2d4+2 piercing, target must succeed DC 11 Strength saving throw or be knocked prone.
\end{description}
\end{minipage}}
\break

\subsubsection*{\underline{4. Steep Passage}}
There is a steep passage leading to \emph{area 6}, and the players can see the bridge in \emph{area 5}. A perception check can be done to spot the goblin hiding on the bridge (contest by the goblin's stealth check).

\subsubsection*{\underline{5. Overpass}}
A single \textbf{goblin} is hiding on the bridge. If he spots the players, he runs to \emph{area 7} which triggers to flood event. Players within 10 ft. of \emph{area 3 or 4} can attempt a DC 10 DEX save, otherwise players must attempt DC 15 STR save or take 1d6 bludgeoning damage from the rushing water.

\subsubsection*{\underline{6. Goblin Den}}
There are \textbf{five goblins} and the second in command Yeemik (goblin with 12hp) in this area. Yeemik wants to get rid of Klarg and become the new leader of the hideout. Yeemik has 15sp and 3 gold teeth worth 1gp each. 

Sildar is held prisoner here, and Yeemik uses him as leverage to convince the players to kill Klarg. Sildar offers 50gp to escort him back to Phandalin.

\subsubsection*{\underline{7. Twin Pools Cave}}
There are \textbf{three goblins} guard the pools used to flood the cave. As soon as a fight breaks out here, one of the goblins flees to warn Klarg in \emph{area 8}.

\subsubsection*{\underline{8. Klarg's Cave}}
There are \textbf{two goblins}, one \textbf{wolf} named Ripper (Klarg's pet) and Klarg the \textbf{bugbear} in this area. If Ripper is killed, Klarg attempts to escape to \emph{area 3} via the chimney. The \textbf{Lionshield Coster supplies} can be found in this room. Among the supplies, there's a treasure chest. 

\colorbox{lightgray}{\begin{minipage}{0.4\textwidth}
\begin{description}
	\item[Klarg, the Bugbear] 
	AC: 16, HP: 27, Speed: 30ft.
	\\ STR[15](+2) 
	\\ DEX[14](+2)
	\\ CON[13](+1)
	\\ INT[8](-1)
	\\ WIS[11](+0)
	\\ CHA[9](-1) 
	\\ Stealth +6, Survival +2, Passive Perception: 10, 200xp
	\\ \textbf{Surprise Attack}: if surprised, target takes an extra 2d6 damage from the attack.
	\\ \textbf{Morningstar}: +4 to hit, 2d8+2 piercing
\end{description}
\end{minipage}}
\break

\emph{\underline{Reward}: Treasure chest containing 600cp, 110sp, \textbf{two potions of healing (heals 2d4+2 hit points)}, and a jade statuette of a frog worth 40gp}

\emph{\underline{Reward}: 275xp for defeating Klarg} 


\subsection*{\underline{NPCs}}
\begin{description}
	\item[Klarg] Bugbear in charge of the Cragmaw hideout, reports to King Grol.
	\item[Sildar Hallwinter] Older human fighter hired by Gundren to escort him in his travels.
	\item[Yeemik] Goblin second in command at the Cragmaw hideout, wants to become leader.
\end{description}